OpenMPIR

### 2017-09-01 paper.tex
Added Stephen's extra tex

All code used for the implementation is available at
\texttt{https://github.com/lanl/openmpir}. The version used for this paper is
tagged as LLVM17.

@@

>>>>

All code used for the implementation is available at \\
\texttt{https://github.com/lanl/openmpir}. The version used for this paper is
tagged as LLVM17.

@@

\section*{Acknowledgment}
Sandia National Laboratories is a multimission laboratory managed and operated 
by National Technology and Engineering Solutions of Sandia, LLC., a wholly 
owned subsidiary of Honeywell International, Inc., for the U.S. Department of 
Energy’s National Nuclear Security Administration under contract DE-NA-0003525.
